|

### 2020-10-01 EvolvertPresent.Rmd
Random changes to improve flow, and comments on the presentation for Olle to follow

---
title: "Badges of status and IR mediated by learning"
author: "Andrés Quiñones"
bibliography: SocialMorphCue.bib
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
    beamer_presentation: 
      fig_caption: yes
      keep_tex: yes
header-includes: 
    \usepackage{float}
    \usepackage{multicol}
    \usepackage{amsmath} 
    \usepackage{graphicx}
    \usepackage{array}
---

@@

## The Hawk-Dove game

Individuals have one of two genetically determined phenotypic strategies. _Hawks_ are willing to start a conflict over resources, while _doves_ prefer to stand down in the hope to share the resource without an aggressive contest.

```{r,echo=FALSE,fig.align="center",out.width='50%'}
knitr::include_graphics("Images//HDgame.png")
```

## The hawk-dove game

\begin{align*}
w_H &= p_H \frac{V-C}{2}+(1-p_h) V\\
w_D &= p_H 0 + (1-p_H)\frac{V}{2}
\end{align*}
\vspace{-0.8cm}
```{r, echo=FALSE,fig.align="center", out.width = '55%'}
knitr::include_graphics("Images//Hawk_dove_plot.png")
```

## What about signals?

```{r,echo=FALSE,fig.align='center',out.height='80%'}
knitr::include_graphics("Images//hosp_alexandra_mackenzie.jpg")

## What about signals?

### When are signals honest?

* Impossible to fake
* Individuals have common interests
* Handicap principle (signal´s cost is proportional to quality)
  + Social costs?

```{r,echo=FALSE, fig.align='center',out.width='100%'}
knitr::include_graphics("Images//social_costs.png")
```

## What about signals?

```{r,echo=FALSE,fig.align='center',out.width='90%'}
knitr::include_graphics("Images//comSystemBot.png")
```

## What about learning?

```{r,echo=FALSE,fig.align='center',out.width='90%'}
knitr::include_graphics("Images//pavlov.jpg")
```

# Associative learning

## Reinforcement learning theory

\begin{columns}[T]
 \column{0.5\linewidth}
 \begin{equation*}
  \Delta V_{t(s)}=\alpha \underbrace{(R_t-V_t)}_\text{prediction error}
  \end{equation*}
  \pause
  \includegraphics[width=1\textwidth]{Images//learn_curve.png}
 \column{0.5\linewidth}
  \pause
  \includegraphics[height=.9\textheight]{Images//predErrorNeur.png}
\end{columns}

## Reinforcement learning theory

```{r,echo=FALSE,fig.align='center',out.width='90%'}
knitr::include_graphics("Images//learnUpdate.png")
```

## Environmental states

### Discrete states
\includegraphics[width=0.8\textwidth]{Images//discreteStates.png}

@@

### Continuos states
\includegraphics[width=0.8\textwidth]{Images//contStates.png}

## Continuos environmental states
\begin{equation*}
  \Delta V_{t(s)}=\alpha \underbrace{(R_t-V_t)}_\text{prediction error}
\end{equation*}

```{r fig2, echo=FALSE, fig.cap="\\label{fig:learning_cartoonRBF}Function approximation for the actor and the critic. Using random values for the responses of each center. Circles show the location of the centers and the maximum response they trigger, while the lines show the total response along the badge size continium.", out.width = '60%'}
knitr::include_graphics("Images/cartoonRBF.png")
```

# Our model

## The hawk-dove game 2.0

\begin{center}
\begin{tabular}{ >{\centering\arraybackslash}p{1cm} | >{\centering\arraybackslash}p{4.5cm} | >{\centering\arraybackslash}p{4.5cm} }
& H & D \\ \hline
H & $p_w V\frac{-C}{2} + (1-p_w) \frac{-C}{2}$ & $V$ \\ \hline
V & $0$ & $\frac{V}{2}$\\
\end{tabular}
\end{center}

\begin{equation*}
p_w=\frac{1}{1+e^{-\beta(Q_i-Q_j)}}
\end{equation*}

```{r,echo=FALSE,fig.align='center',out.width='50%'}
par(plt=posPlot(),las=1)
plot(logist(seq(-1,1,length.out = 1000),alpha = 0,beta = 2)~
       seq(-1,1,length.out = 1000),type="l",xlab="Difference in quality",
     ylab = expression(p[w]),cex.lab=2,lwd=3,col="red",cex.axis=2,ylim=c(0,1))
lines(logist(seq(-1,1,length.out = 1000),alpha = 0,beta = 10)~
       seq(-1,1,length.out = 1000),lwd=3,col="green")
legend("topleft",legend=c(2,10),col=c("red","green"),lwd=3,title = expression(beta),cex=2,bty="n")

## Sender Code

\begin{equation*}
s_i = \frac{1}{1+e^{-(\epsilon_i+\gamma_iQ_i)}}
\label{eq:react_norm}
\end{equation*}

```{r,echo=FALSE,fig.align='center',out.width='50%'}
par(plt=posPlot(),las=1)
plot(logist(seq(0,1,length.out = 1000),alpha = 2,beta = 4)~
       seq(0,1,length.out = 1000),type="l",xlab="Quality",
     ylab = expression(p[w]),cex.lab=2,lwd=3,col="red",cex.axis=2,ylim=c(0,1))
lines(logist(seq(0,1,length.out = 1000),alpha = 5,beta = 10)~
       seq(0,1,length.out = 1000),lwd=3,col="green")
legend("topleft",legend=c(4,10),col=c("red","green"),lwd=3,title = expression(gamma),cex=2,bty="n")

## Receiver code

\begin{equation*}
  \Delta V_{t(s)}=\alpha (R_t-V_t)
\end{equation*}

```{r, echo=FALSE,fig.align='center', out.width = '60%'}
knitr::include_graphics("Images/cartoonRBF.png")
```

## Learning can mediate the evolution of Badges of Status
### Variation among replicates
```{r, echo=FALSE,fig.align='center', out.width='100%'}
knitr::include_graphics("Simulations/betCostEvol1_/evolDynAll_betCost5.png")
```

## Learning can mediate the evolution of Badges of Status
### Individual replicates: Badges
```{r, echo=FALSE,fig.align='center', out.width='100%'}
knitr::include_graphics("Simulations/betCostEvol1_/evolDyn0_betCost5.png")
```

## Learning can mediate the evolution of Badges of Status
### Individual replicates: no badges
```{r, echo=FALSE,fig.align='center', out.width='100%'}
knitr::include_graphics("Simulations/betCostEvol1_/evolDyn5_betCost5.png")
```

## The effect of costs on Badges of Status
### Behavioural interactions

```{r, echo=FALSE,fig.align='center', out.width='100%'}
knitr::include_graphics("Simulations/betCostEvol1_/BehavIntALL.png")
```

>>>>

---
title: "Badges of status and Individual Recognition mediated by learning"
author: "Andrés Quiñones"
bibliography: SocialMorphCue.bib
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
    beamer_presentation: 
      fig_caption: yes
      keep_tex: yes
header-includes: 
    \usepackage{float}
    \usepackage{multicol}
    \usepackage{amsmath} 
    \usepackage{graphicx}
    \usepackage{array}
---

<!-- ## The need to choose a partner and an action -->

<!-- ```{r,echo=FALSE,fig.align="center",out.width='40%',fig.show='hold'} -->
<!-- knitr::include_graphics("Images/sexSelec.jpg") -->
<!-- knitr::include_graphics("Images/begging.jpg") -->
<!-- knitr::include_graphics("Images/broodparasite.jpg") -->
<!-- knitr::include_graphics("Images/dominance.jpg") -->
<!-- ``` -->

<!-- ## Animal communication -->

<!-- ```{r,echo=FALSE,fig.align="center",out.width='80%'} -->
<!-- knitr::include_graphics("Images/monkey_mobile.jpeg") -->
<!-- ``` -->

<!-- ## The cost of aggression -->

<!-- ```{r,echo=FALSE,fig.align="center",out.width='80%'} -->
<!-- knitr::include_graphics("Images/harm.jpg") -->
<!-- ``` -->

<!-- ## What about signals? -->

<!-- ### Badge of status -->

<!-- ```{r,echo=FALSE,fig.align='center',out.height='80%'} -->
<!-- knitr::include_graphics("Images//hosp_alexandra_mackenzie.jpg") -->

<!-- ``` -->

<!-- ## What about signals? -->

<!-- ### When are signals honest? -->

<!-- * Impossible to fake -->
<!-- * Individuals have common interests -->
<!-- * Handicap principle (signal´s cost is proportional to quality) -->

<!-- ## What about signals? -->

<!-- ### Individual recognition -->

<!-- ```{r,echo=FALSE,fig.align='center',out.height='70%'} -->
<!-- knitr::include_graphics("Images//indRecog.png") -->

<!-- ``` -->
<!-- [@tibbetts_Individual_2007] -->

<!-- ## What about signals? -->

<!-- ### BS or IR? -->

<!-- ```{r,echo=FALSE,fig.align='center',out.height='75%'} -->
<!-- knitr::include_graphics("Images//IRvsBS.png") -->

<!-- ``` -->
<!-- [@sheehan_There_2016] -->

<!-- ## What about signals? -->

<!-- ```{r,echo=FALSE,fig.align='center',out.width='90%'} -->
<!-- knitr::include_graphics("Images//comSystemBot.png") -->
<!-- ``` -->

<!-- ## What about learning? -->

<!-- ```{r,echo=FALSE,fig.align='center',out.width='90%'} -->
<!-- knitr::include_graphics("Images//pavlov.jpg") -->
<!-- ``` -->

<!-- # Associative learning -->

<!-- ## Reinforcement learning theory -->

<!-- \begin{columns}[T] -->
<!--  \column{0.5\linewidth} -->
<!--  \begin{equation*} -->
<!--   \Delta V_{t(s)}=\alpha \underbrace{(R_t-V_t)}_\text{prediction error} -->
<!--   \end{equation*} -->
<!--   \pause -->
<!--   \includegraphics[width=1\textwidth]{Images//learn_curve.png} -->
<!--  \column{0.5\linewidth} -->
<!--   \pause -->
<!--   \includegraphics[height=.9\textheight]{Images//predErrorNeur.png} -->
<!-- \end{columns} -->

<!-- ## Reinforcement learning theory -->

<!-- ```{r,echo=FALSE,fig.align='center',out.width='90%'} -->
<!-- knitr::include_graphics("Images//learnUpdate.png") -->
<!-- ``` -->

<!-- ## The Hawk-Dove game -->

<!-- Individuals have one of two genetically determined phenotypic strategies. _Hawks_ are willing to start a conflict over resources, while _doves_ prefer to stand down in the hope to share the resource without an aggressive contest. -->

<!-- ```{r,echo=FALSE,fig.align="center",out.width='50%'} -->
<!-- knitr::include_graphics("Images//HDgame.png") -->
<!-- ``` -->

<!-- \begin{align*} -->
<!-- w_H &= p_H \frac{V-C}{2}+(1-p_h) V\\ -->
<!-- w_D &= p_H 0 + (1-p_H)\frac{V}{2} -->
<!-- \end{align*} -->
<!-- \vspace{-0.8cm} -->
<!-- ```{r, echo=FALSE,fig.align="center", out.width = '55%'} -->
<!-- knitr::include_graphics("Images//Hawk_dove_plot.png") -->
<!-- ``` -->

<!-- ## Environmental states -->

<!-- ### Discrete states -->
<!-- \includegraphics[width=0.8\textwidth]{Images//discreteStates.png} -->

<!-- \pause -->

<!-- ### Continuos states -->
<!-- \includegraphics[width=0.8\textwidth]{Images//contStates.png} -->

<!-- ## Continuos environmental states -->
<!-- \begin{equation*} -->
<!--   \Delta V_{t(s)}=\alpha \underbrace{(R_t-V_t)}_\text{prediction error} -->
<!-- \end{equation*} -->

<!-- ```{r fig2, echo=FALSE, fig.cap="\\label{fig:learning_cartoonRBF}Function approximation for the actor and the critic. Using random values for the responses of each center. Circles show the location of the centers and the maximum response they trigger, while the lines show the total response along the badge size continium.", out.width = '60%'} -->
<!-- knitr::include_graphics("Images/cartoonRBF.png") -->
<!-- ``` -->

<!-- # Our model -->

<!-- ## The hawk-dove game 2.0 -->

<!-- \begin{center} -->
<!-- \begin{tabular}{ >{\centering\arraybackslash}p{1cm} | >{\centering\arraybackslash}p{4.5cm} | >{\centering\arraybackslash}p{4.5cm} } -->
<!-- & H & D \\ \hline -->
<!-- H & $p_w V\frac{-C}{2} + (1-p_w) \frac{-C}{2}$ & $V$ \\ \hline -->
<!-- V & $0$ & $\frac{V}{2}$\\ -->
<!-- \end{tabular} -->
<!-- \end{center} -->

<!-- \begin{equation*} -->
<!-- p_w=\frac{1}{1+e^{-\beta(Q_i-Q_j)}} -->
<!-- \end{equation*} -->

<!-- ```{r,echo=FALSE,fig.align='center',out.width='50%'} -->
<!-- par(plt=posPlot(),las=1) -->
<!-- plot(logist(seq(-1,1,length.out = 1000),alpha = 0,beta = 2)~ -->
<!--        seq(-1,1,length.out = 1000),type="l",xlab="Difference in quality", -->
<!--      ylab = expression(p[w]),cex.lab=2,lwd=3,col="red",cex.axis=2,ylim=c(0,1)) -->
<!-- lines(logist(seq(-1,1,length.out = 1000),alpha = 0,beta = 10)~ -->
<!--        seq(-1,1,length.out = 1000),lwd=3,col="green") -->
<!-- legend("topleft",legend=c(2,10),col=c("red","green"),lwd=3,title = expression(beta),cex=2,bty="n") -->

<!-- ``` -->

<!-- ## Sender Code -->

<!-- \begin{equation*} -->
<!-- s_i = \frac{1}{1+e^{-(\epsilon_i+\gamma_iQ_i)}} -->
<!-- \label{eq:react_norm} -->
<!-- \end{equation*} -->

<!-- ```{r,echo=FALSE,fig.align='center',out.width='50%'} -->
<!-- par(plt=posPlot(),las=1) -->
<!-- plot(logist(seq(0,1,length.out = 1000),alpha = 2,beta = 4)~ -->
<!--        seq(0,1,length.out = 1000),type="l",xlab="Quality", -->
<!--      ylab = expression(p[w]),cex.lab=2,lwd=3,col="red",cex.axis=2,ylim=c(0,1)) -->
<!-- lines(logist(seq(0,1,length.out = 1000),alpha = 5,beta = 10)~ -->
<!--        seq(0,1,length.out = 1000),lwd=3,col="green") -->
<!-- legend("topleft",legend=c(4,10),col=c("red","green"),lwd=3,title = expression(gamma),cex=2,bty="n") -->

<!-- ``` -->

<!-- ## Receiver code -->

<!-- \begin{equation*} -->
<!--   \Delta V_{t(s)}=\alpha (R_t-V_t) -->
<!-- \end{equation*} -->

<!-- ```{r, echo=FALSE,fig.align='center', out.width = '60%'} -->
<!-- knitr::include_graphics("Images/cartoonRBF.png") -->
<!-- ``` -->

@@

Learning simulations (without evolution yet), the sender code is set as an honest signal.
Receivers develop a threshold like response according to their quality

## Learning can mediate the evolution of Badges of Status
### Variation among replicates
\small
set of simulations with the badge working as a handicap (cost inversely proportional to quality)

```{r, echo=FALSE,fig.align='center', out.width='100%'}
knitr::include_graphics("Simulations/betCostEvol1_/evolDynAll_betCost5.png")
```

## Learning can mediate the evolution of Badges of Status
### Individual replicates: Badges
\small
One of the replicates of the previous slide, the badge as a handicap
```{r, echo=FALSE,fig.align='center', out.width='100%'}
knitr::include_graphics("Simulations/betCostEvol1_/evolDyn0_betCost5.png")
```

## Learning can mediate the evolution of Badges of Status
### Individual replicates: Badges
\small
Panels show the changes in frequency distribution along evolution ($\alpha$, $\beta$, and resulting badge respectively) for the replicate shown in the previous slide

```{r, echo=FALSE,fig.align='left', out.height='28%',fig.show='hold', fig.cap="alpha - beta -Badge"}
knitr::include_graphics("Simulations/betCostEvol1_/evolDistAlpha0_betCost5.png")
knitr::include_graphics("Simulations/betCostEvol1_/evolDistBeta0_betCost5.png")
knitr::include_graphics("Simulations/betCostEvol1_/evolDistBadge0_betCost5.png")
```

## Learning can mediate the evolution of Badges of Status
### Individual replicates: no badges
\small
One of the replicates where the badge did not evolve

```{r, echo=FALSE,fig.align='center', out.width='100%'}
knitr::include_graphics("Simulations/betCostEvol1_/evolDyn5_betCost5.png")
```

## The effect of costs on Badges of Status
### Behavioural interactions
\small
Colours correspond to replicates, each point is one snapshot on the second half of the simulations.
Higher costs seem to favour the signalling equilibrium

```{r, echo=FALSE,fig.align='center', out.width='80%'}
knitr::include_graphics("Simulations/betCostEvol1_/BehavIntALL.png")
```
## The effect of costs on Badges of Status
### Badge size
\small
Same as previous slide but for the resulting signal. Higher costs yield smaller averga sizes and smaller ranges.

```{r, echo=FALSE,fig.align='center', out.width='80%'}
knitr::include_graphics("Simulations/betCostEvol1_/CueALL.png")
```

## The evolution of cheap Badges of Status
### Variation among replicates
\small
Here simulations where the signal has no cost

```{r, echo=FALSE,fig.align='center', out.width='80%'}
knitr::include_graphics("Simulations/nIntGroupEvol1_/evolDynALL_nIntGroup2000.png")
```

## The evolution of cheap Badges of Status
### Variation within a replicate
\small
Here simulations where the signal has no cost.

There seems to be some consistency in the three type of sender codes

```{r, echo=FALSE,fig.align='center', out.width='80%'}
knitr::include_graphics("Simulations/nIntGroupEvol1_/evolDyn8_nIntGroup2000.png")
```

## The evolution of cheap Badges of Status
### Variation within a replicate

\tiny
Panels show the changes in frequency distribution along evolution ($\alpha$, $\beta$, and resulting badge respectively) for the replicate shown in the previous slide

Branching events in the reaction norm parameters yield three types of sender codes. One (more or less)
honest, two dishonest (one with a big badge and one with a small badge)

```{r, echo=FALSE,fig.align='left', out.height='28%',fig.show='hold', fig.cap="alpha - beta -Badge"}
knitr::include_graphics("Simulations/nIntGroupEvol1_/evolDistAlpha8_nIntGroup2000.png")
knitr::include_graphics("Simulations/nIntGroupEvol1_/evolDistBeta8_nIntGroup2000.png")
knitr::include_graphics("Simulations/nIntGroupEvol1_/evolDistBadge8_nIntGroup2000.png")
```

## The evolution of cheap Badges of Status
### How often does it happen?
\tiny
Values of $\alpha$ and $\beta$ for each individual in the different replicates. Each dot an individual,
each panel a replicate. Individuals are sampled from populations from the second half of the simulations.

Individuals in some simulations split up in three groups, others in two groups; 
in one simulation the population does not split up

```{r, echo=FALSE,fig.align='left', out.width='90%',fig.show='hold'}
knitr::include_graphics("Simulations/nIntGroupEvol1_/corrAlphBet_nIntGroup2000.png")
```

## The evolution of cheap Badges of Status
### Does it matter?
\small
Behavioural interactions splitting up the replicates according to the number of "types" that 
evolve

```{r, echo=FALSE,fig.align='left', out.width='90%',fig.show='hold'}
knitr::include_graphics("Simulations/nIntGroupEvol1_/BehavIntAllClusters_nIntGroup2000.png")
```

## Interaction structures - do they matter?

```{r, echo=FALSE,fig.align='center', out.width='100%',}
knitr::include_graphics("Images/networks.png")
```
[@chaine_Manipulating_2018]

## Localized interaction structures

### Costly signals 
\tiny
Behavioural interactions and badge size for simulations with costs where individuals interact in small groups. On the $x$ axes number of different individuals each focal interacts with.

```{r, echo=FALSE,fig.align='center', out.width='90%',fig.show='hold'}
knitr::include_graphics("Simulations/nIntGroupCost_/BehavIntALL.png")
knitr::include_graphics("Simulations/nIntGroupCost_/CueALL.png")
```

## Localized interaction structures

### Cheap signals (free)
\small
Variation among individuals in different replicates (just like before) in replicates where individuals interact with 10 other individuals.

A part from replicates with two clusters, the clustering seems less straightforward as before

```{r, echo=FALSE,fig.align='center', out.width='85%',fig.show='hold'}
knitr::include_graphics("Simulations/nIntGroupEvol1_/corrAlphBet_nIntGroup10.png")
```

## Localized interaction structures

### Cheap signals (free)

\small
Behavioural interactions for the replicates form previous slide. I split up the replicates according to clusters (despite clusters not being clear cut).

Only replicates with only one cluster seems to have less aggressive interactions

```{r, echo=FALSE,fig.align='center', out.width='90%',fig.show='hold'}
knitr::include_graphics("Simulations/nIntGroupEvol1_/BehavIntAllClusters_nIntGroup10.png")
```

## Localized interaction structures

### Cheap signals or Individual recognition?
\tiny
In these set, I changed the learning set up, I increased the number of centers (10 now, 6 before)
along the signal axis; and I reduced the level or generalization.

There seems to be an effect on the slope of the reaction norm. It stays very close to zero.

```{r, echo=FALSE,fig.align='center', out.width='90%',fig.show='hold'}
knitr::include_graphics("Simulations/nIntGroupCenters1_/evolDynALL_nIntGroup10.png")
```

## Localized interaction structures

### Cheap signals or Individual recognition
\small
Same replicates as the previous slide. Variation in $\beta$ and $\alpha$ among individuals for different replicates.

No clear clustering. Variation mostly along the $\alpha$ axis

```{r, echo=FALSE,fig.align='center', out.width='90%',fig.show='hold'}
knitr::include_graphics("Simulations/nIntGroupCenters1_/corrAlphBet_nIntGroup10.png")
```
## Localized interaction structures

### Cheap signals or Individual recognition?
\small
Panels show the changes in frequency distribution along evolution ($\alpha$, $\beta$, and resulting badge respectively) for the replicate shown in the previous slide.

$\beta$ around zero, $\alpha$ all over the place.

```{r, echo=FALSE,fig.align='left', out.height='28%',fig.show='hold'}
knitr::include_graphics("Simulations/nIntGroupCenters1_/evolDistAlpha5_nIntGroup10.png")
knitr::include_graphics("Simulations/nIntGroupCenters1_/evolDistBeta5_nIntGroup10.png")
knitr::include_graphics("Simulations/nIntGroupCenters1_/evolDistBadge5_nIntGroup10.png")
```

<!-- ## Aqui vamos! mirar correlaciones de 20 y 2000 luego interacciones -->

<!-- ## Comparar scenarios -->

## Why would you want to be recognized?

@@

### The peaceful, the aggressive and the clever

- Learning initial conditions

\tiny
Here, I vary the aggressive tendency for unlearned individuals in these three set ups.

Agressive, peaceful, clever (starts at the ESS of the classic hawk-dove game)

```{r, echo=FALSE,fig.align='left', out.width='90%',fig.show='hold'}
knitr::include_graphics("Images/cartoonRBF_InitAct.png")
```

## Why would you want to be recognized?

### The peaceful

Variation among replicates

```{r, echo=FALSE,fig.align='left', out.width='100%',fig.show='hold'}
knitr::include_graphics("Simulations/initAct_/evolDynALL_initAct2.png")
```

## Why would you want to be recognized?

### The peaceful

Variation within one replicate

```{r, echo=FALSE,fig.align='left', out.width='100%',fig.show='hold'}
knitr::include_graphics("Simulations/initAct_/evolDyn2_initAct2.png")
```

## Why would you want to be recognized?

### The peaceful

Changes in the frequency distributions

```{r, echo=FALSE,fig.align='left', out.height='28%',fig.show='hold'}
knitr::include_graphics("Simulations/initAct_/evolDistAlpha2_initAct2.png")
knitr::include_graphics("Simulations/initAct_/evolDistBeta2_initAct2.png")
knitr::include_graphics("Simulations/initAct_/evolDistBadge2_initAct2.png")
```

## Why would you want to be recognized?

### The peaceful

Favours variation and cheap signals

```{r, echo=FALSE,fig.align='left', out.width='100%',fig.show='hold'}
knitr::include_graphics("Simulations/initAct_/corrAlphBet_initAct2.png")
```

## Why would you want to be recognized?

### The aggressive

Variation among replicates

```{r, echo=FALSE,fig.align='left', out.width='100%',fig.show='hold'}
knitr::include_graphics("Simulations/initAct_/evolDynALL_initAct-2.png")
```

## Why would you want to be recognized?

### The aggressive

Variation within one replicate

```{r, echo=FALSE,fig.align='left', out.width='100%',fig.show='hold'}
knitr::include_graphics("Simulations/initAct_/evolDyn0_initAct-2.png")
```

## Why would you want to be recognized?

### The aggressive

Disfavours variation and signal evolution - no signalling

```{r, echo=FALSE,fig.align='left', out.width='100%',fig.show='hold'}
knitr::include_graphics("Simulations/initAct_/corrAlphBet_initAct-2.png")
```

## Why would you want to be recognized?

### The clever (ESS)

Variation among replicates

```{r, echo=FALSE,fig.align='left', out.width='100%',fig.show='hold'}
knitr::include_graphics("Simulations/initAct_/evolDynALL_initAct-0.69.png")
```

## Why would you want to be recognized?

### The clever (ESS)

Variation within one replicate

```{r, echo=FALSE,fig.align='left', out.width='100%',fig.show='hold'}
  knitr::include_graphics("Simulations/initAct_/evolDyn0_initAct-0.69.png")
```

## Why would you want to be recognized?

### The clever (ESS)

Signal evolution seems to be driven by drift. Most replicates end up in one of the two extremes

```{r, echo=FALSE,fig.align='left', out.width='100%',fig.show='hold'}
  knitr::include_graphics("Simulations/initAct_/corrAlphBet_initAct-0.69.png")
```

## Take-home messages

### Costly signals
- Learning can mediate costly signals
- More expensive signals seem be more likely to evolve
- Less expensive signals provide more information
- Local interactions do not impede the evolution of costly signals (as has been suggested)

### Cheap signals
- Learning mediates the evolution of polymorphisms with "honest" and "dishonest"
individuals
- Under local interactions learning seems to allow the evolution of IR
- Cheap signals depend on the innate level of aggression (before learning) of individuals
- Peace begets heterogeneity, aggression begets homogeneity

## Questions?

```{r, echo=FALSE,fig.align='center', out.height='80%',fig.show='hold'}
  knitr::include_graphics("Images/BizarroParrot.jpg")
```

## References

### 2020-10-01 manuscript_1.0.Rmd
Random changes to improve flow, and comments on the presentation for Olle to follow

---
title: |
  | Learning can mediate both badges of status and individual recognition
author:
- Andrés E. Quiñones^[Laboratorio de Biología Evolutiva de Vertebrados, Departamento
  de Ciencias Biológicas, Universidad de los Andes, Bogotá, Colombia]
- C. Daniel Cadena*
- Olof Leimar^[Department of Zoology, Stockholm University, Stockholm, Sweden]
- Redouan Bshary^[Institute of Biology, University of Neuchâtel, Neuchâtel, Switzerland]
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  word_document: default
  pdf_document: default
fig_caption: yes
fontsize: 12pt
header-includes:
- \usepackage{float}
- \usepackage{setspace}\doublespacing
- \linespread{2}
- \usepackage{lineno}
- \linenumbers
keep_tex: yes
keywords: My keywords
linespread: 2
bibliography: SocialMorphCue.bib
spacing: double
style: C:\Users\andre\Zotero\styles\elife.csl
abstract: Learning rules.
---

@@

Associative learning is a key cognitive mechanism that allows individuals to associate
rewards with environmental stimuli and appropriate behavior [@staddon_Adaptive_2016]. 
Since it was originally described, associative learning has been found in all major
vertebrate taxon, and many invertebrates [@heyes_Simple_2012;
@macphail_Brain_1982; @staddon_Adaptive_2016; @behrens_Associative_2008].
Using these associations to respond to environmental changes is particularly adaptive in
complex environments [@dridi_Environmental_2016]. Besides its wide taxonomic and
ecological relevance, associative learning has shown to be a flexible cognitive mechanism
that can be tuned to different roles depending on the ecological situation 
[@enquist_Power_2016; @quinones_Reinforcement_2019]. Despite all this, associative 
learning is not often included in evolutionary explanations 
[@fawcett_Exposing_2013; @kamil_Optimal_1983; @mcauliffe_Psychology_2015]. 
Computational models of evolution can play an important role to overcome the 
lack of integration between learning and evolution. Reinforcement learning theory 
encompases a series of computational methods inspired on the psychological and 
neurological mechanisms of associative learning [@sutton_Reinforcement_2018].
These set of algorithms allow the implementation of biologically realistic problems, 
capturing the essence of learning processes [@frankenhuis_Enriching_2018; @quinones_Reinforcement_2019]. 
Furthermore, these algorithms can be embebed in evolutionary simulations in order 
to have theoretical predictions of the effect that learning can have in behavioral [@leimar_Learning_2019]
and morphological evolution.

In here we present an evolutionary model where individuals use associative learning 
to develop a tendency to behave aggressively (or  peacefully), in the context of
competition over resoureces, depending on the quantitative morphological trait 
they perceive in their opponent (badge). Over evolutionary time individuals evolve
the size of their badge, and whether it depends on their quality. Under this simple
set up, individuals can use the badge both as a signal of quality (BS)
or as a trait for IR. We use the model to asses under what conditions of interaction
structure we expect different communication signals evolve.

>>>>

---
title: |
  | Learning can mediate both badges of status and individual recognition
author:
- Andrés E. Quiñones^[Laboratorio de Biología Evolutiva de Vertebrados, Departamento
  de Ciencias Biológicas, Universidad de los Andes, Bogotá, Colombia]
- C. Daniel Cadena*
- Olof Leimar^[Department of Zoology, Stockholm University, Stockholm, Sweden]
- Redouan Bshary^[Institute of Biology, University of Neuchâtel, Neuchâtel, Switzerland]
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document: default
  word_document: default
fig_caption: yes
fontsize: 12pt
header-includes:
- \usepackage{float}
- \usepackage{setspace}\doublespacing
- \linespread{2}
- \usepackage{lineno}
- \linenumbers
keep_tex: yes
keywords: My keywords
linespread: 2
bibliography: SocialMorphCue.bib
spacing: double
style: C:\Users\andre\Zotero\styles\elife.csl
abstract: Adaptive behavioural responses often depend on qualities of the interacting partner of an individual. For example, when competing for resources, an individual might be better off escalating fights with individuals of lower quality, while restraining from fighting individuals of higher quality. Communication systems involving signals of quality allow individuals to reduce uncertainty regarding the fighting ability of their partners and make more adaptive behavioral decisions. However, dishonest individuals can destabilize such communications systems. One open question is whether cognitive mechanisms, such as learning, can maintain the honesty of signals, thus, favoring their evolutionary stability. Here we present evolutionary simulations, where individuals can produce a signal proportional to their quality; and learn along their lifetime the best response to the signal emitted by their peers. In these simulations, learning on the receiver side can mediate the evolution of signals of quality on the sender side. When the cost of the signal is proportional to the quality of the sender populations are only composed of honest signalers. When the cost is not proportional to the quality of the signaler, the population is composed of both honest and dishonest signalers. We argue that learning can be a general cognitive mechanism playing a role in a wide range of communication systems.  
---

@@

Associative learning is a key cognitive mechanism that allows individuals to associate
rewards with environmental stimuli and appropriate behavior [@staddon_Adaptive_2016]. 
Since it was originally described, associative learning has been found in all major
vertebrate taxon, and many invertebrates [@heyes_Simple_2012;
@macphail_Brain_1982; @staddon_Adaptive_2016; @behrens_Associative_2008].
Using these associations to respond to environmental changes is particularly adaptive in
complex environments [@dridi_Environmental_2016]. Besides its wide taxonomic and
ecological relevance, associative learning has shown to be a flexible cognitive mechanism
that can be tuned to different roles depending on the ecological situation 
[@enquist_Power_2016; @quinones_Reinforcement_2019]. Despite all this, associative 
learning is not often included in evolutionary explanations 
[@fawcett_Exposing_2013; @kamil_Optimal_1983; @mcauliffe_Psychology_2015]. 
Computational models of evolution can play an important role to overcome the 
lack of integration between learning and evolution. Reinforcement learning theory 
encompass a series of computational methods inspired on the psychological and 
neurological mechanisms of associative learning [@sutton_Reinforcement_2018].
These set of algorithms allow the implementation of biologically realistic problems, 
capturing the essence of learning processes [@frankenhuis_Enriching_2018; @quinones_Reinforcement_2019]. 
Furthermore, these algorithms can be embedded in evolutionary simulations in order 
to have theoretical predictions of the effect that learning can have in behavioral [@leimar_Learning_2019]
and morphological evolution.

In here we present an evolutionary model where individuals use associative learning 
to develop a tendency to behave aggressively (or  peacefully), in the context of
competition over resources, depending on the quantitative morphological trait 
they perceive in their opponent (badge). Over evolutionary time individuals evolve
the size of their badge, and whether it depends on their quality. Under this simple
set up, individuals can use the badge both as a signal of quality (BS)
or as a trait for IR. We use the model to asses under what conditions of interaction
structure we expect different communication signals evolve.
